Interval Probability for Fuzzy Quantum Theories

### 2016-05-13 prob.tex
prob.tex \subsection{Quantum Probability Measures} Add an example...

\begin{definition}[Projection Operators; Orthogonality~\cite{10.2307/2308516,Redhead1987-REDINA,peres1995quantum,Swart2013}]
Given a Hilbert space $\Hilb$, an event\footnote{An event is formally called an experimental proposition~\cite{BirkhoffVonNeumann1936},
a question~\cite{10.2307/2308516,DBLP:journals/corr/abs-0910-2393}, or an
elementary quantum test~\cite{peres1995quantum}} mathematically is represented as a projection operator $P:\Hilb\rightarrow\Hilb$ onto a linear subspace~$S$ of $\Hilb$. The set of all
events can be defined recursively as follow:
\footnote {``Projection'' is sometimes called
``orthogonal projection" or ``self-adjoint projection" to
emphasize $P^{\dagger} = P$~\cite{Maassen2010}.}
\begin{itemize}
\item $\mathbb{0}$ is a projection.
\item For any vector $\ket{\psi}\in \Hilb$,
  $\frac{\proj{\psi}}{\ip{\psi}{\psi}}$ is a projection.
\item Projection operators $P_1$ and $P_2$ are orthogonal if $P_1P_2 =
  P_2P_1 = \mathbb{0}$. The sum of two orthogonal projections~$P_1 +
  P_2$ is also a projection. Moreover, if $P_1$ and $P_2$ project onto
  subspaces $S_1$ and $S_2$ respectively, then $P_1 + P_2$ will project onto the
  linear span of $S_1$ and $S_2$, i.e., $\left\{\ket{\psi_1} + \ket{\psi_2}
  \middle| \ket{\psi_1}\in S_1 \textrm{ and } \ket{\psi_2}\in S_2 \right\}$.
\end{itemize}
\end{definition}

@@

\begin{definition}[Quantum Probability Space~\cite{10.2307/2308516,gleason1957,Redhead1987-REDINA,Maassen2010}]
  Given a Hilbert space $\Hilb$, a \emph{quantum probability space}
  consists of a set of events $\events$ and a probability measure
  $\mu : \events \rightarrow [0,1]$ such that:\footnote {It is
    possible to define a more general space of events consisting of
    all operators~$\mathcal{A}$ on $\Hilb$ and consider
    $\mu:\mathcal{A}\rightarrow\C$~\cite{Maassen2010,Swart2013}.  When
    an operator $A\in\mathcal{A}$ is Hermitian, $\mu\left(A\right)$ is
    the expectation value of $A$. We does not take this approach
    because we want to focus only on probability. }
\begin{itemize}
\item The set of events consists of all projections. This set includes
  the empty projection, projection operators $\proj{\psi}$ for each
  state $\ket{\psi}$, sums of \emph{orthogonal} projections, and
  products of \emph{commuting} projections; 
\item $\mu(\mathbb{1})=1$, and 
\item for mutually orthogonal projections $E_i$, we have
  $\mu\left(\sum_{i}E_{i}\right)=\sum_{i}\mu\left(E_{i}\right)$.
\end{itemize}
\qed\end{definition}

@@

For a given set of events $\events$, there are many possible
probability measures $\mu : \events \rightarrow [0,1]$. The Born rule,
a postulate of quantum mechanics, states that each quantum state
$\ket{\phi}$ induces a probability measure $\mu_\phi$ as follows:
\[ 
\mu_\phi(E) = \ip{\phi}{E\phi}
\]
Conversely, Gleason's theorem states that given a probability measure
$\mu$, there exist a quantum state $\ket{\phi}$ that induces such a
measure using the Born rule. The theorem is only valid in Hilbert
spaces with dimension $d \geq 3$. It is instructive to study
counterexamples in $d=2$, i.e., the case of a one-qubit
system. Consider five states $\ket{\psi_0}$ to $\ket{\psi_4}$ that
form five orthogonal bases $\{ \ket{\psi_0}, \ket{\psi_1} \}$,
$\{ \ket{\psi_1}, \ket{\psi_2} \}$,
$\{ \ket{\psi_2}, \ket{\psi_3} \}$,
$\{ \ket{\psi_3}, \ket{\psi_4} \}$, and
$\{ \ket{\psi_4}, \ket{\psi_0} \}$ and consider the probability
measure defined as follows. For all $i \in \{0,1,2,3,4\}$, we have
$\mu_X(\proj{\psi_i}) = 1/2$. For each orthogonal basis, the
probability is 1 as desired and yet it is impossible to find a single
quantum state that realizes such a probability
measure (see \url{http://tph.tuwien.ac.at/~svozil/publ/2006-gleason.pdf})

>>>>

\begin{definition}[Projection Operators; Orthogonality~\cite{10.2307/2308516,Redhead1987-REDINA,peres1995quantum,Swart2013}]
\label{def:Projection} Given a Hilbert space $\Hilb$, an event\footnote{An event
is formally called an experimental proposition~\cite{BirkhoffVonNeumann1936}, a question~\cite{10.2307/2308516,DBLP:journals/corr/abs-0910-2393}, or an
elementary quantum test~\cite{peres1995quantum}} mathematically is represented as a projection operator $P:\Hilb\rightarrow\Hilb$ onto a linear subspace~$S$ of $\Hilb$. The set of all
events can be defined recursively as follow:
\footnote {``Projection'' is sometimes called
``orthogonal projection" or ``self-adjoint projection" to
emphasize $P^{\dagger} = P$~\cite{Maassen2010}.}
\begin{itemize}
\item $\mathbb{0}$ is a projection.
\item For any vector $\ket{\psi}\in \Hilb$,
  $\frac{\proj{\psi}}{\ip{\psi}{\psi}}$ is a projection.
\item Projection operators $P_1$ and $P_2$ are orthogonal if $P_1P_2 =
  P_2P_1 = \mathbb{0}$. The sum of two orthogonal projections~$P_1 +
  P_2$ is also a projection. Moreover, if $P_1$ and $P_2$ project onto
  subspaces $S_1$ and $S_2$ respectively, then $P_1 + P_2$ will project onto the
  linear span of $S_1$ and $S_2$, i.e., $\left\{\ket{\psi_1} + \ket{\psi_2}
  \middle| \ket{\psi_1}\in S_1 \textrm{ and } \ket{\psi_2}\in S_2 \right\}$.
\end{itemize}
\end{definition}

@@

\begin{definition}[Quantum Probability Space~\cite{10.2307/2308516,gleason1957,Redhead1987-REDINA,Maassen2010}]
  Given a Hilbert space $\Hilb$, a \emph{quantum probability space}
  consists of a set of events $\events$ and a probability measure
  $\mu : \events \rightarrow [0,1]$ such that:\footnote {It is
    possible to define a more general space of events consisting of
    all operators~$\mathcal{A}$ on $\Hilb$ and consider
    $\mu:\mathcal{A}\rightarrow\C$~\cite{Maassen2010,Swart2013}.  When
    an operator $A\in\mathcal{A}$ is Hermitian, $\mu\left(A\right)$ is
    the expectation value of $A$. We does not take this approach
    because we want to focus only on probability. }
\begin{itemize}
\item The set of events consists of all projections as in
  definition~\ref{def:Projection};
\item $\mu(\mathbb{1})=1$, and 
\item for mutually orthogonal projections $E_i$, we have
  $\mu\left(\sum_{i}E_{i}\right)=\sum_{i}\mu\left(E_{i}\right)$.
\end{itemize}
\qed\end{definition}

@@

For a given set of events $\events$, there are many possible probability
measures $\mu:\events\rightarrow[0,1]$. The Born rule~\cite{Born1984,Mermin2007},
a postulate of quantum mechanics, states that each pure quantum state
$\ket{\phi}$ induces a probability measure $\mu_{\phi}$ as follows:
\[
\mu_{\phi}(E)=\ip{\phi}{E\phi}
\]
Moreover, the Born rule can be extended to a mixed state~$\rho$.
If the density matrix of a mixed state~$\rho$ can be expressed as
a convex combination of pure states, i.e., $\rho=\sum_{j=1}^{N}q_{j}\proj{\psi_{j}}$,
where $\sum_{j=1}^{N}q_{j}=1$, then the probability measure induced
by $\rho$ can be expressed as a convex combination as well~\cite{peres1995quantum,544199}:
\begin{eqnarray}
\mu_{\rho}\left(E\right) & = & \Tr\left(\rho E\right)=\sum_{j=1}^{N}q_{j}\mu_{\psi_{j}}\left(E\right)\textrm{ .}\label{BornRule.mixed}
\end{eqnarray}

Conversely, Gleason's theorem states that given a probability measure
$\mu$, there exist a mixed state~$\rho$ that induces such a measure
using the Born rule. The theorem is only valid in Hilbert spaces with
dimension $d\geq3$. It is instructive to study counterexamples in
$d=2$, i.e., the case of a one-qubit system.

\begin{example}[One-qubit quantum probability measure] 
Consider a quantum probability
measure~$\mu:\events\rightarrow[0,1]$ defined as follow:
\[
\mu(E)=\begin{cases}
1 & \textrm{, if }E=\proj{\ps}\textrm{ ;}\\
0 & \textrm{, if }E=\proj{\ms}\textrm{ ;}\\
\mu_{\ket{0}}(E) & \textrm{, otherwise.}
\end{cases}
\]
On one hand, $\mu$ is a probability measure. Because $\mu$ is almost
the same as $\mu_{\ket{0}}$ which is a probability measure, we only
need to check $E=\proj{\ps}$ and $E=\proj{\ms}$. $\proj{\ps}$ and
$\proj{\ms}$ are only orthogonal to each other, and we have 
\[
\mu(\proj{\ps})+\mu(\proj{\ms})=1+0=1
\]
which satisfies the conditions as a probability measure. On the other
hand, $\mu$ cannot be induced by any mixed state because 
\[
\mu(\proj{\ps})=\mu(\proj{0})=1\textrm{ .}
\]
However, $\mu_{\rho}(E)=1$ if and only if $\rho$ represents a pure
state and $\rho=E$.
\qed\end{example}
